---
title: "VAST14 Statistical Review"
author: "Paul Klemm"
date: "18. November 2015"
output: 
  html_document:
    toc: true
---

This notebooks conducts a statistical analysis of hypotheses derived through the VAST'14 publication [Interactive Visual Analysis of Image-Centric Cohort Study Data](http://dx.doi.org/10.1109/tvcg.2014.2346591).

Sources are:

- [https://stats.stackexchange.com/questions/108007/correlations-with-categorical-variables](https://stats.stackexchange.com/questions/108007/correlations-with-categorical-variables)
- [http://www.analyticsforfun.com/2014/06/performing-anova-test-in-r-results-and.html](http://www.analyticsforfun.com/2014/06/performing-anova-test-in-r-results-and.html)
- [https://stats.stackexchange.com/questions/12398/how-to-interpret-f-and-p-value-in-anova](https://stats.stackexchange.com/questions/12398/how-to-interpret-f-and-p-value-in-anova)
- [https://stats.stackexchange.com/questions/147863/how-to-interpret-the-residual-colors-on-a-mosaic-plot](https://stats.stackexchange.com/questions/147863/how-to-interpret-the-residual-colors-on-a-mosaic-plot)
- Mosaic Plot Residual Shading [https://cran.r-project.org/web/packages/vcd/vignettes/residual-shadings.pdf](https://cran.r-project.org/web/packages/vcd/vignettes/residual-shadings.pdf)

## Setup

Load the data and only keep subjects with extracted centerlines. This is necessary to have a concurrent population with the paper.

```{r results='hide', message=FALSE}
library(gplots)
library(jsonlite)
library(dplyr)
library(vcd)
library(gridExtra)
```

```{r}
# Get all subjects IDs with centerlines
centerlines <- list.files('/Users/paul/Sites/vis14/site/data/centerlines')
# Replace the centerlines to leave only the subject IDs
centerlines <- gsub(pattern = '_MESH_COR_ES.vtk', replacement = '', centerlines)
#'/Users/paul/Sites/vis14/site/data/ship-data/data/shipdata/s0-t0_correlations.json'
# Now read both SHIP cohorts and only keep the subjects with a centerline
ship_s2 <- read.csv('/Users/paul/Sites/vis14/site/data/ship-data/data/shipdata/SHIP_2013_174_D_S2_complete/SHIP_2013_174_D_S2_complete.csv')
ship_t0 <- read.csv('/Users/paul/Sites/vis14/site/data/ship-data/data/shipdata/SHIP_2013_174_D_T0_complete/SHIP_2013_174_D_T0_complete.csv')
# Rename dimension names
same_features <- fromJSON('same_features.json')
for (rename_feature in same_features) {
  names(ship_t0)[names(ship_t0)==rename_feature$name_t0] <- rename_feature$newName
  names(ship_s2)[names(ship_s2)==rename_feature$name_s2] <- rename_feature$newName
}
ship <- merge(ship_s2, ship_t0, all = TRUE)
# Only keep subjects with an extracted centerline (https://stackoverflow.com/questions/9860090/in-r-why-is-better-than-subset)
ship <- ship[ship$zz_nr %in% centerlines, ]

# Filter Subjects above 60
# TODO: Continue here
ship_age <- filter(ship, Age > 60)
```

## ANOVA for `Back Pain` and `Age`.

At first, display the means between the groups.

**H_0** There is no difference in `Back Pain` regarding `Age`.

**H_1** The `Back Pain` groups are *not* equal w.r.t. `Age`.

```{r fig.width=10, fig.height=8}
par(mfrow=c(2,2), oma=c(1,1,2,1), mar=c(2,2,2,2))
plotmeans(ship$Age ~ ship$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of Age by back pain")

boxplot(ship$Age ~ ship$Rueckenschmerz_3Monate, main="Back pain by age (mean is black dot)", xlab="back pain", ylab="age", col=rainbow(7))

plotmeans(ship_age$Age ~ ship_age$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of Age by back pain")

boxplot(ship_age$Age ~ ship_age$Rueckenschmerz_3Monate, main="Back pain by age (mean is black dot)", xlab="back pain", ylab="age", col=rainbow(7))

title(main = "Top: Age by Back Pain; Bottom: Subjects older than 60 years", outer=TRUE)
```

The few outliers may distort the analysis, therefore I remove them.
```{r fig.width=10, fig.height=8}
# Convert back pain to a factor variable
ship$Rueckenschmerz_3Monate <- as.factor(ship$Rueckenschmerz_3Monate)
ship_age$Rueckenschmerz_3Monate <- as.factor(ship_age$Rueckenschmerz_3Monate)
# Analyze only for subjects with valid back pain indicators
ship_valid_backpain <- filter(ship, !(as.character(Rueckenschmerz_3Monate)%in% c("99996", "99998", "99999")))
ship_age_valid_backpain <- filter(ship_age, !(as.character(Rueckenschmerz_3Monate)%in% c("99996", "99998", "99999")))
ship_valid_backpain <- droplevels(ship_valid_backpain)
ship_age_valid_backpain <- droplevels(ship_age_valid_backpain)
```

Apply the same plot again.

```{r fig.width=10, fig.height=8}
par(mfrow=c(2,2), oma=c(1,1,2,1), mar=c(2,2,2,2))
plotmeans(ship_valid_backpain$Age ~ ship_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of Age by back pain")

boxplot(ship_valid_backpain$Age ~ ship_valid_backpain$Rueckenschmerz_3Monate, main="Back pain by age (mean is black dot)", xlab="back pain", ylab="age", col=rainbow(7))

plotmeans(ship_age_valid_backpain$Age ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of Age by back pain")

boxplot(ship_age_valid_backpain$Age ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, main="Back pain by age (mean is black dot)", xlab="back pain", ylab="age", col=rainbow(7))

title(main = "Top: Age by Back Pain; Bottom: Subjects older than 60 years", outer=TRUE)
```

Calculate the ANOVA for both data sets.

```{r fig.width=10, fig.height=8}
summary(aov(formula = Age~Rueckenschmerz_3Monate, data = ship))
summary(aov(formula = Age~Rueckenschmerz_3Monate, data = ship_valid_backpain))
summary(aov(formula = Age~Rueckenschmerz_3Monate, data = ship_age))
summary(aov(formula = Age~Rueckenschmerz_3Monate, data = ship_age_valid_backpain))
```

Neither of the features are suitable to confirm the alternative hypothesis. Help with the interpretation can be found here:

- [http://www.analyticsforfun.com/2014/06/performing-anova-test-in-r-results-and.html](http://www.analyticsforfun.com/2014/06/performing-anova-test-in-r-results-and.html)
- [https://stats.stackexchange.com/questions/12398/how-to-interpret-f-and-p-value-in-anova](https://stats.stackexchange.com/questions/12398/how-to-interpret-f-and-p-value-in-anova)

## ANOVA for `Back Pain` and `Body Fat`

At first, plot again the means as well as create the boxplots.

```{r fig.width=10, fig.height=8}
par(mfrow=c(2,2), oma=c(1,1,2,1), mar=c(2,2,2,2))
plotmeans(ship_valid_backpain$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of body fat by back pain", xlab="back pain", ylab="body fat")

boxplot(ship_valid_backpain$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_valid_backpain$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

plotmeans(ship_age_valid_backpain$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of body fat by back pain", xlab="back pain", ylab="body fat")

boxplot(ship_age_valid_backpain$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

title(main = "Top: Age by Body Fat; Bottom: Subjects older than 60 years", outer=TRUE)
```

The boxplot shows that there are most likely error codes still in the `body fat` group, which are therefore removed.

```{r fig.width=10, fig.height=8}
ship_valid_backpain_bodyfat <- filter(.data = ship_valid_backpain, BIA_KOERPERFETT_KORR_IN_PROZ < 90000)

ship_age_valid_backpain_bodyfat <- filter(.data = ship_age_valid_backpain, BIA_KOERPERFETT_KORR_IN_PROZ < 90000)

par(mfrow=c(1,2), oma=c(1,1,2,1), mar=c(2,2,2,2))
boxplot(ship_valid_backpain_bodyfat$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_valid_backpain_bodyfat$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

boxplot(ship_age_valid_backpain_bodyfat$BIA_KOERPERFETT_KORR_IN_PROZ ~ ship_age_valid_backpain_bodyfat$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

summary(aov(formula = BIA_KOERPERFETT_KORR_IN_PROZ~Rueckenschmerz_3Monate, data = ship_valid_backpain_bodyfat))

summary(aov(formula = BIA_KOERPERFETT_KORR_IN_PROZ~Rueckenschmerz_3Monate, data = ship_age_valid_backpain_bodyfat))
```

The p value is very low with a high F value, therefore we can accept the alternative hypothesis.

## ANOVA for `Back Pain` and `Body Weight`

At first, plot again the means as well as create the boxplots.

```{r fig.width=10, fig.height=8}
par(mfrow=c(2,2), oma=c(1,1,2,1), mar=c(2,2,2,2))

plotmeans(ship_valid_backpain$Gewicht ~ ship_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of body fat by back pain", xlab="back pain", ylab="body fat")

boxplot(ship_valid_backpain$Gewicht ~ ship_valid_backpain$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

plotmeans(ship_age_valid_backpain$Gewicht ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, digits=2, ccol="red", mean.labels=T, main="Plot of body fat by back pain", xlab="back pain", ylab="body fat")

boxplot(ship_age_valid_backpain$Gewicht ~ ship_age_valid_backpain$Rueckenschmerz_3Monate, main="back pain by body fat (mean is black dot)", xlab="back pain", ylab="body fat", col=rainbow(7))

title(main = "Top: Age by Body Weight; Bottom: Subjects older than 60 years", outer=TRUE)

summary(aov(formula = Gewicht~Rueckenschmerz_3Monate, data = ship_valid_backpain))
summary(aov(formula = Gewicht~Rueckenschmerz_3Monate, data = ship_age_valid_backpain))
```

The ANOVA rejects the alternative hypothesis.

## Cramérs V for `Back Pain` and `High Blood Pressure`

Since both features are categorical, the statistic of choice is Cramérs V. At first, look at the mosaic plot.

```{r fig.width=10, fig.height=8}
tab_standard <- xtabs(~Blutdruck_hoch + Rueckenschmerz_3Monate, data = ship_valid_backpain)
tab_age <- xtabs(~Blutdruck_hoch + Rueckenschmerz_3Monate, data = ship_age_valid_backpain)
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Blutdruck_hoch="High Blood Pressure", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Blutdruck_hoch="High Blood Pressure (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)

```

`Blood pressure` shows some error markers, which are removed before conducting the Cramérs V analysis.

```{r fig.width=10, fig.height=8}
ship_valid_backpain_bloodpressure <- filter(.data = ship_valid_backpain, Blutdruck_hoch < 900)
ship_age_valid_backpain_bloodpressure <- filter(.data = ship_age_valid_backpain, Blutdruck_hoch < 900)
tab_standard <- xtabs(~Blutdruck_hoch + Rueckenschmerz_3Monate, data = 
ship_valid_backpain_bloodpressure)
tab_age <- xtabs(~Blutdruck_hoch + Rueckenschmerz_3Monate, data = 
ship_age_valid_backpain_bloodpressure)
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Blutdruck_hoch="High Blood Pressure", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Blutdruck_hoch="High Blood Pressure (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)
summary(assocstats(tab_standard))
summary(assocstats(tab_age))
```

Cramérs V is very low and therefore, no correlation can be observed.

## Cramérs V for `Back Pain` and `Alcohol Intake in the last 12 month`

Create a mosaic plot first.

```{r fig.width=10, fig.height=8}
# Create Tabs
tab_standard <- xtabs(~Haeufigkeit_Alkohol_12Monate + Rueckenschmerz_3Monate, data = ship_valid_backpain)
tab_age <- xtabs(~Haeufigkeit_Alkohol_12Monate + Rueckenschmerz_3Monate, data = ship_age_valid_backpain)

# Plot Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Haeufigkeit_Alkohol_12Monate="Alcohol Intake in last 12 Month", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Haeufigkeit_Alkohol_12Monate="Alcohol Intake in last 12 Month (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)
```

Remove the error values

```{r fig.width=10, fig.height=8}
# Filter Subjects
ship_valid_backpain_alcohol <- filter(.data = ship_valid_backpain, Haeufigkeit_Alkohol_12Monate < 900)
ship_age_valid_backpain_alcohol <- filter(.data = ship_age_valid_backpain, Haeufigkeit_Alkohol_12Monate < 900)

# Create Tables
tab_standard <- xtabs(~Haeufigkeit_Alkohol_12Monate + Rueckenschmerz_3Monate, data = ship_valid_backpain_alcohol)
tab_age <- xtabs(~Haeufigkeit_Alkohol_12Monate + Rueckenschmerz_3Monate, data = ship_age_valid_backpain_alcohol)

# Plot Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Haeufigkeit_Alkohol_12Monate="Alcohol Intake in last 12 Month", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Haeufigkeit_Alkohol_12Monate="Alcohol Intake in last 12 Month (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)

# Calculate Correlations
summary(assocstats(tab_standard))
summary(assocstats(tab_age))
```

Again a very low value, no correlation found.

## Cramérs V for `Back Pain` and `Attentiveness Problems`

Create a mosaic plot first.

```{r fig.width=10, fig.height=8}
# Create Tables
tab_standard <- xtabs(~Konzentrationsschwaeche + Rueckenschmerz_3Monate, data = ship_valid_backpain)
tab_age <- xtabs(~Konzentrationsschwaeche + Rueckenschmerz_3Monate, data = ship_age_valid_backpain)

# Plot Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Konzentrationsschwaeche="Attentiveness Disorder", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Konzentrationsschwaeche="Attentiveness Disorder (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)
```

Remove the error values

```{r fig.width=10, fig.height=8}
# Remove the Errors Values
ship_valid_backpain_attentive <- filter(.data = ship_valid_backpain, Konzentrationsschwaeche < 900)
ship_age_valid_backpain_attentive <- filter(.data = ship_age_valid_backpain, Konzentrationsschwaeche < 900)

# Create Tabs
tab_standard <- xtabs(~Konzentrationsschwaeche + Rueckenschmerz_3Monate, data = ship_valid_backpain_attentive)
tab_age <- xtabs(~Konzentrationsschwaeche + Rueckenschmerz_3Monate, data = ship_age_valid_backpain_attentive)

# Create Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Konzentrationsschwaeche="Attentiveness Disorder", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Konzentrationsschwaeche="Attentiveness Disorder (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)

# Calculate Correlations
summary(assocstats(tab_standard))
summary(assocstats(tab_age))
```

The plot actually shows a low relationship of `attentiveness problems` and `back pain`.

## Cramérs V of `Amount of Sleep` and `Back Pain`

First, create the mosaic plot.

```{r fig.width=10, fig.height=8}
# Calculate Tabs
tab_standard <- xtabs(~Hohes_Schlafbeduerfnis + Rueckenschmerz_3Monate, data = ship_valid_backpain)
tab_age <- xtabs(~Hohes_Schlafbeduerfnis + Rueckenschmerz_3Monate, data = ship_age_valid_backpain)

# Plot Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Hohes_Schlafbeduerfnis="High Amount of Sleep", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Hohes_Schlafbeduerfnis="High Amount of Sleep (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)
```

Remove the error values and conduct the analysis.

```{r fig.width=10, fig.height=8}
# Remove Error Values
ship_valid_backpain_sleep <- filter(.data = ship_valid_backpain, Hohes_Schlafbeduerfnis < 900)
ship_age_valid_backpain_sleep <- filter(.data = ship_age_valid_backpain, Hohes_Schlafbeduerfnis < 900)

# Create Tables
tab_standard <- xtabs(~Hohes_Schlafbeduerfnis + Rueckenschmerz_3Monate, data = ship_valid_backpain_sleep)
tab_age <- xtabs(~Hohes_Schlafbeduerfnis + Rueckenschmerz_3Monate, data = ship_age_valid_backpain_sleep)

# Plot Mosaics
mosaic_standard <- grid.grabExpr(mosaic(tab_standard, shade=TRUE, legend=TRUE, set_varnames = list(Hohes_Schlafbeduerfnis="High Amount of Sleep", Rueckenschmerz_3Monate="Back Pain")))
mosaic_age <- grid.grabExpr(mosaic(tab_age, shade=TRUE, legend=TRUE, set_varnames = list(Hohes_Schlafbeduerfnis="High Amount of Sleep (Age > 60 years)", Rueckenschmerz_3Monate="Back Pain (Age > 60 years)")))
grid.arrange(mosaic_standard, mosaic_age, ncol=2)

# Calculate Correlations
summary(assocstats(tab_standard))
summary(assocstats(tab_age))
```